---
title: "Analysing the 2024 U.S. Presidential Election"
subtitle: "Spotlight on North Carolina's Role as a Battleground State"
author: 
  - David Qi
  - Haobo Ren
  - Ruikang Wang
thanks: "Code and data are available at: https://"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(knitr)
library(ggplot2)
```


# Introduction {#sec-intro}

Many people think that only Asians are obsessed with tea, but after the UK passed tea around the world, North America are beginning to embrace the culture of tea.  This paper will examine the price of green tea among various suppliers, explore the reasons for the price changes, and study the pattern of price changes among various supermarkets through the vehicle of green tea.



# Data {#sec-data}


```{r}
#| label: tbl-polloverview
#| tbl-cap: Comparison of average polling result for two candiates
#| include: true
#| echo: false
#| warning: false
#| message: false

merged_summary = merged_summary %>% select(state,total_count.x,mean_pct_harris,mean_pct_trump,abs_diff)  %>% arrange(abs_diff)

kable(merged_summary, col.names = c("State", "Number of Polls" , "Average Support Rate(Harris)","Average Support Rate(Trump)","Absolute difference"))
```
 
# Results {#sec-results}


# Discussion{#sec-discussion}


\newpage

\appendix


\newpage

# References



